---
title: "Classroom Manuscript"
author: Mona Zhu
date: Updated July 4 2019
output: 
  html_document:
    fig_width: 8
    fig_height: 5
    fig.align: center
    toc: true
    toc_float: true
    theme: cerulean
    highlight: tango
    code_folding: hide
    warning: true
    message: false
---

<style>
pre code, pre, code {
  overflow-y: auto !important;
  max-height: 20em;
}
</style>


```{r, message=F}
# Packages 
library(openxlsx)
library(lme4)
library(reshape2)
library(ez)
library(plyr)
library(ggplot2)
library(gridExtra)
library(sjPlot)
```

```{r}
# raw data file with both chosen and simulated random seats
comb<-read.xlsx("C:/Users/MonaZhu/Dropbox/CANB Lab/Classroom (new)/Complete Classroom Data_FULLDATA_21Mar2017.xlsx",
                sheet = 1)
comb$LogonDate<-convertToDate(comb$LogonDate)
comb$UserName=factor(round(comb$UserName, 0)) 
comb$ClassFreq<-factor(ifelse(comb$Year=="W2015"|comb$Year=="F2015", "Once", "Twice"))
comb$ClassType<-factor(comb$ClassType)
comb$ClassType<-factor(comb$ClassType, levels(comb$ClassType)[c(2,1)])
comb$Year<-factor(comb$Year)
comb$Year<-factor(comb$Year, levels(comb$Year)[c(1,4,2,3)])
comb$MovedFromPrev<-ifelse(comb$DistFromPrev<.1, 1, 0) # 1 = same seats; 0 = different seats
comb$Condition=factor(comb$Condition)
comb$Condition=factor(comb$Condition, levels(comb$Condition)[c(2,1)])
comb$ID<-factor(paste0(comb$UserName, comb$Year))
comb<-comb[c(15, 1:14)]

comb$FinalExam<-factor(ifelse(comb$LogonDate=="2014-12-01"|
                                  comb$LogonDate=="2015-04-01"|
                                  comb$LogonDate=="2015-12-01"|
                                  comb$LogonDate=="2016-03-31"|
                                  comb$LogonDate=="2017-03-30", "Yes", "No"))

comb$Week<-car::recode(comb$Time, "1=2; 3=2;
                         8=9; 10=9;
                         15=16; 17=16;
                         22=23; 24=23;
                         29=30; 31=30;
                         36=37; 38=37;
                         43=44; 45=44;
                         50=51; 52=51; 
                         57=58; 59=58; 
                         64=65; 66=65;
                         71=72; 73=72; 
                         78=79; 80=79;
                         85=86; 87=86")


# subset that excludes "day 1" as there is no data
comb.sub<-subset(comb, Time!=1 & Condition=="Chosen") 

# subset of data frame containing on individuals' actual seat selection (i.e., exclude simulated random seat selection)
comb.c<-NULL

# calculating time interval between each class
for (id in levels(comb.sub$ID)){
  data<-subset(comb.sub, ID==id)
  for (i in 1:nrow(data)) {
    data$Interval[i]<-ifelse(data$Time[i]==data$Time[1], 
                          data$Time[i]-1, 
                          data$Time[i]-data$Time[i-1])
  }
  comb.c<-rbind(comb.c, data)  
}

once<-subset(comb.c, ClassFreq=="Once")
twice<-subset(comb.c, ClassFreq=="Twice")
sub<-subset(comb.c, FinalExam=="No")

comb.c$Time.c<-comb.c$Time - mean(comb.c$Time)
comb.c$Time2.c<-(comb.c$Time.c)^2
comb.c$Order.c<-comb.c$Order - mean(comb.c$Order)

once$Time.c<-once$Time - mean(once$Time)
once$Time2.c<-(once$Time.c)^2
once$Order.c<-once$Order - mean(once$Order)

twice$Time.c<-twice$Time - mean(twice$Time)
twice$Time2.c<-(twice$Time.c)^2
twice$Order.c<-twice$Order - mean(twice$Order)

sub$Time.c<-sub$Time - mean(sub$Time)
sub$Time2.c<-(sub$Time.c)^2
sub$Order.c<-sub$Order - mean(sub$Order)
```


```{r}
ex<-subset(comb.c, ClassType=="Exam")
lec<-subset(comb.c, 
            LogonDate=="2014-09-22"|
              LogonDate=="2014-10-08"|
              LogonDate=="2014-10-27"|
              LogonDate=="2014-11-10"|
              LogonDate=="2014-11-26"|
              LogonDate=="2015-02-04"|
              LogonDate=="2015-03-25"|
              LogonDate=="2015-10-13"|
              LogonDate=="2015-11-24"|
              LogonDate=="2016-01-19"|
              LogonDate=="2016-02-09"|
              LogonDate=="2016-03-01"|
              LogonDate=="2016-03-15"|
              LogonDate=="2016-03-29")

lecex<-rbind(lec, ex)

lecex$ExamType<-factor(ifelse(lecex$LogonDate=="2014-11-26"|lecex$LogonDate=="2014-12-01"|lecex$LogonDate=="2015-03-25"|lecex$LogonDate=="2015-04-01"|lecex$LogonDate=="2015-11-24"|lecex$LogonDate=="2015-12-01"|lecex$LogonDate=="2016-03-29"|lecex$LogonDate=="2016-03-31", "Final", "Midterm"))

```


## Descriptives

There are a total of `r length(unique(comb.c$ID))` observations and `r length(unique(comb.c$UserName))` unique users in the study

## Examining Distance From Previous Seat 

### Linear Mixed Model Analysis 

#### MAIN Linear analysis:

```{r}
linear<-lmer(DistFromPrev~Time.c+Order.c+(1|UserName), data = comb.c, REML=F, na.action="na.omit")
tab_model(linear, transform=NULL, show.stat = T, p.val = "wald", digits = 3)
```


#### Linear model PER INDIVIDUAL

```{r}
# ind<-NULL
# for (id in levels(comb.c$UserName)){
#   subs<-comb.c[comb.c$UserName==id,]
#   if (nrow(subs)<2){
#     next
#   } else {
#     coef<-lm(DistFromPrev~Time+Order, data = subs, na.action="na.omit")$coefficients
#     ind<-rbind(ind, coef) 
#   }
# }
# 
# ind2<-as.data.frame(ind[complete.cases(ind),])
# ind2$negslope<-ifelse(ind2$Time<0, 1, 0)
# mean(ind2$negslope)
# ind2$posslope<-ifelse(ind2$Order>0, 1, 0)
# ind2$both<-ifelse(ind2$negslope==1 & ind2$posslope==1, 1, 0)
# mean(ind2$both)

```



##### Proportion of people choosing the same seat

```{r}
prop<-glmer(MovedFromPrev~Time.c+Order.c+(1|UserName), data=comb.c, family=binomial(link="logit"),
            na.action = na.omit) 

tab_model(prop, transform=NULL, show.stat = T, p.val = "wald", digits = 3)

```


#### Proportion of people NOT choosing the same seat

```{r}
nonzero<-subset(comb.c, MovedFromPrev==0)
nonzero$Time.c<-nonzero$Time - mean(nonzero$Time)
nonzero$Order.c<-nonzero$Order - mean(nonzero$Order)

linear0<-lmer(DistFromPrev~Time.c+Order.c+(1|UserName), data = nonzero, REML=F, na.action="na.omit")
tab_model(linear0, transform=NULL, show.stat = T, p.val = "wald", digits = 3)
```

#### MAIN Curvilinear analysis:

```{r}
curvilinear<-lmer(DistFromPrev~Time.c+Order.c+Time2.c+(1|UserName), data = comb.c, REML=F, na.action="na.omit")
tab_model(curvilinear, transform=NULL, show.stat = T, p.val = "wald", digits = 3)
```

#### Model To Include for Paper
```{r}
tab_model(linear, curvilinear, transform=NULL, show.stat = T, p.val = "wald", digits = 4,
          dv.labels = c("Linear Model", "Curvilinear Model"),
          pred.labels = c("Intercept", "Time", "Order", "Time^2"),
          show.aic = T)
```

#### Model Comparison:

```{r}
anova(linear, curvilinear)
```


### Removing Last Day and comparing linear vs curvilinear model

```{r}
curvilinear2<-lmer(DistFromPrev~Time.c+Order.c+Time2.c+(1|UserName), data = sub, REML=F, na.action="na.omit")
tab_model(curvilinear2, transform=NULL, show.stat = T, p.val = "wald", digits = 5)
```

```{r}
# linear2<-lmer(DistFromPrev~Time+Order+(1|UserName), data = sub, REML=F, na.action="na.omit")
# anova(linear2, curvilinear2)
```

### Removing First 2 weeks

```{r}
# sub2<-subset(sub, Time>=22)
# 
# lin.sub2<-lmer(DistFromPrev~Time+Order+(1|UserName), data = sub2, REML=F, na.action="na.omit")
# summary(lin.sub2)

```

### Graph of seating distance as a function of time {.tabset}

#### Overall (Scatterplot + Means)

```{r}
comb_table<-plyr::count(comb.c, c("Time", "DistFromPrev"))
comb.new<-merge(comb.c, comb_table, by=c("Time", "DistFromPrev"), all.x=T, all.y=F)

graph1=ddply(comb.new, c("ID", "Week"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
# head(graph1)
graph2=ddply(graph1, c("Week"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
# print(graph2)

# png(file = "Classroom_Figure2_Updated_7Jan2020.png", bg = "white", type = c("cairo"), width=2400, height=2200, res=300)

plot1<-
  ggplot(comb.new, aes(x=Time, y=DistFromPrev)) +
  geom_point(aes(size=freq), alpha=0.2, show.legend = F, colour="grey")+
  geom_smooth(method=lm, formula = y ~ x + I(x^2), se=F, fullrange=TRUE, colour="gray55", alpha=.7)+
  geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="gray30", linetype="dotdash")+
  geom_point(data = graph2, aes(x=Week, y=dep.avg), size=3.5, shape=17)+
  # facet_grid(Year~.)+
  theme(panel.background= element_rect(fill=NA), 
        plot.background = element_rect(fill=NA, colour=NA),
        axis.ticks.x=element_blank(),
        panel.border = element_rect(fill="transparent", colour="grey60"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.margin=unit(c(.5,.5,0,1), "cm"))+
  # geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="black", linetype="dotted")+
  # geom_smooth(method=lm, formula=y ~ poly(x,2), colour="maroon", se=T, fullrange=TRUE)+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1))+
  coord_cartesian(xlim=c(0,88))


graph3=ddply(comb.new, c("ID", "Week"), function(df)
  return(c(dep.avg=mean(df$MovedFromPrev, na.rm=T)))) # change DV
graph4=ddply(graph3, c("Week"), function(df)
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
# print(graph2)

plot2<-ggplot(graph4, aes(x=Week, y=dep.avg))+
  geom_bar(position = "dodge", stat = "identity", fill="grey60")+
  theme(panel.background= element_rect(fill=NA),
        plot.background = element_rect(fill=NA, colour=NA),
        axis.ticks.x=element_blank(),
        panel.border = element_rect(fill="transparent", colour="transparent"),
        # axis.line = element_line(colour="grey60"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin=unit(c(0,.5,0.5,1), "cm")
        )+
  scale_x_continuous("Time (Days)", position = 'bottom')+
  geom_hline(yintercept=0, colour="grey60")+
  geom_vline(xintercept= -4.1, colour="grey60", size=.2)+
  scale_y_continuous("Proportion Individuals \nChoosing Same Seat", expand=c(0,0), limits=c(0, 0.6))+
  coord_cartesian(xlim=c(0,88))


# png(file = "Classroom_Figure1_Updated_23Jul2019.png", bg = "transparent", type = c("cairo"), width=2400, height=1400, res=300)
  
cowplot::plot_grid(plot1, plot2, align = "v", nrow = 2, rel_heights = c(.7, .3), labels="AUTO",label_size = 16)

# dev.off()

```



## Exam vs. Lecture Day

```{r}
melted<-melt(lecex, id=c(1:9, 12:22))
casted<-dcast(melted, ID+UserName+Year~ClassType+ExamType, mean, subset=.(variable=="DistFromPrev"), na.rm=T)

final<-casted[complete.cases(casted),]
remelt<-melt(final, id=1:3)
remelt$variable=as.character(remelt$variable)
remelt$ClassType<- factor(as.character(sapply(strsplit(remelt$variable, split='_', fixed=TRUE), function(x) (x[1]))))
remelt$ExamType<- factor(as.factor(sapply(strsplit(remelt$variable, split='_', fixed=TRUE), function(x) (x[2]))))
remelt$variable<-NULL
names(remelt)[4]="DistFromPrev"
remelt$ID=factor(remelt$ID)

remelt$ClassType<-factor(remelt$ClassType, levels(remelt$ClassType)[c(2,1)])
```

```{r}
mod<-lmer(DistFromPrev~ExamType*ClassType+(1|UserName), data = remelt, REML=F, na.action="na.omit",
          contrasts=list(ExamType="contr.sum", ClassType="contr.sum"))
# mod2<-lmer(DistFromPrev~ExamType*ClassType+(1|UserName), data = lecex, REML=F, na.action="na.omit",
#           contrasts=list(ExamType="contr.sum", ClassType="contr.sum"))

tab_model(mod, transform=NULL, show.stat = T, p.val = "wald", digits = 2)

mod3<-lmer(DistFromPrev~ClassType+(1|UserName), data = remelt[remelt$ExamType=="Midterm",],
          REML=F, na.action="na.omit")
mod4<-lmer(DistFromPrev~ClassType+(1|UserName), data = remelt[remelt$ExamType=="Final",],
          REML=F, na.action="na.omit")
tab_model(mod3, mod4, transform=NULL, show.stat = T, p.val = "wald", digits = 2)

amod<-ezANOVA(data=remelt, wid=.(ID), dv=.(DistFromPrev), within=.(ExamType, ClassType), type=3,
              detailed=T)
amod


```

Breaking it down and looking at just the seating distance prior to and on the day of exam for (1) midterm/unit exams and (2) final exam

```{r}
m<-t.test(final$Lecture_Midterm, final$Exam_Midterm, paired=T)
effsize::cohen.d(final$Lecture_Midterm, final$Exam_Midterm, paired=T, hedges.correction=T)
f<-t.test(final$Lecture_Final, final$Exam_Final, paired=T)
effsize::cohen.d(final$Lecture_Final, final$Exam_Final, paired=T, hedges.correction=T)

```


```{r}
graph1=ddply(remelt, c("ID", "ClassType", "ExamType"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
# head(graph1)
graph2=ddply(graph1, c("ExamType", "ClassType"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
print(graph2)

p.val<-c(f$ p.value, m$ p.value)
round(p.adjust(p.val, "bonferroni"), 3)

```

corrected Bonferroni p value: `r `


#### Graph

```{r}
err=amod$ANOVA$SSd/amod$ANOVA$DFd

png(file = "Classroom_Figure2.png", bg = "transparent", type = c("cairo"), width=2400, height=1600, res=300)

# change variable name (aov.1, aov.2, reg.1, reg.2)
ggplot(graph2, aes(x=ExamType, y=dep.avg, group=ClassType, colour=ClassType))+   
  geom_point(size=3, shape=16, position = position_dodge(0.5))+
  geom_errorbar(aes(ymax=dep.avg+sqrt(err[4])*qt(0.975,df=dep.count-1)/sqrt(dep.count), 
                    ymin=dep.avg-sqrt(err[4])*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.10, position = position_dodge(0.5))+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="black"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="grey60"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="black"),
    legend.key = element_rect(fill = "transparent", colour = "transparent")
    )+
  scale_colour_manual("Class", values=c("gray15","gray60"))+
  scale_x_discrete("", labels=c("Final Unit Exam", "Other Unit Exams"))+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 0.5)
                     ,limits=c(0.6,3.1)
  )+
  annotate("text", size=12, x=1, y=3,, colour="grey30", label="*")

dev.off()

```




### ADDITIONAL ANALYSES


#### People entered in as an additional factor
```{r}
numppl<-count(comb.c, c("Year", "Time"))
comb.ppl<-merge(comb.c, numppl, by=c("Year", "Time"), all.x=T, all.y=F)
plot(comb.ppl$DistFromPrev~comb.ppl$freq)

ppl.mod<-lmer(DistFromPrev ~ Time+Order+freq+(1|UserName), data = comb.ppl[comb.ppl$freq<18,], na.action = "na.omit", method="ML")
summary(ppl.mod)
```

#### Interval between classes
```{r}
# remove intervals greater than 7
# interval<-subset(comb.c, !(Interval>8))
days.mod1<-lme(DistFromPrev ~ Interval, random= ~1|UserName, data = interval, na.action = "na.omit", method="ML")
days.mod2<-lme(DistFromPrev ~ Time+Order+Interval, random= ~1+Time|UserName, data = interval, na.action = "na.omit", method="ML")
```

```{r}
graph1=ddply(comb.c, c("ID", "Interval"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
head(graph1)
graph2=ddply(graph1, c("Interval"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
# print(graph2)
graph2<-graph2[complete.cases(graph2),]

ggplot(graph2, aes(x=Interval, y=dep.avg))+   
  # geom_line()+
  geom_point(size=4, shape=17, position = position_dodge(0.5))+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="#432620"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="#432620"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="#432620"),
    legend.key = element_rect(fill = "transparent", colour = "transparent")
  )
  # scale_colour_manual(values=c("gray15","gray60"))+
  # scale_x_continuous("Time (Days)")+
  # scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1), limits=c(0,4))
  # geom_smooth(data = comb.c, aes(x = Time, y = DistFromPrev), method=lm, se=T, fullrange=TRUE, colour="lightseagreen")

  
```



### OTHER GRAPHS/ANALYSES 

```{r}
graph1=ddply(comb.c, c("ID", "Time"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
head(graph1)
graph2=ddply(graph1, c("Time"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
# print(graph2)


ggplot(graph2, aes(x=Time, y=dep.avg))+   
  geom_line()+
  geom_point(size=4, shape=17, position = position_dodge(0.5))+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="#432620"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="#432620"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="#432620"),
    legend.key = element_rect(fill = "transparent", colour = "transparent")
  )+
  # scale_colour_manual(values=c("gray15","gray60"))+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1)
                     , limits=c(0,4))+
  geom_smooth(data = comb.c, aes(x = Time, y = DistFromPrev), method=lm, se=T, fullrange=TRUE, colour="lightseagreen")

  
```



#### By Course

```{r}
graph1=ddply(comb.c, c("ID", "Time", "Year", "ClassType"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
graph2=ddply(graph1, c("Time", "Year", "ClassType"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
print(graph2)

# change variable name (aov.1, aov.2, reg.1, reg.2)
ggplot(graph2, aes(x=Time, y=dep.avg, group=Year))+   
  geom_line()+
  geom_point(size=3.5, shape=17, position = position_dodge(0.5), aes(colour=ClassType))+
  facet_grid(Year~.)+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="#432620"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="#432620"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="#432620"),
    legend.key = element_rect(fill = "transparent", colour = "transparent")
    # ,legend.position="none"
  )+
  scale_colour_manual("Class Type", values=c("gray15","gray60"))+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1)
                     , limits=c(0.1,4.2)
  )
```

#### Once A Week Classes Combined Only

```{r}
comb_table<-count(once, c("Time", "DistFromPrev"))
comb.new<-merge(once, comb_table, by=c("Time", "DistFromPrev"), all.x=T, all.y=F)

graph1=ddply(once, c("ID", "Time"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
# head(graph1)
graph2=ddply(graph1, c("Time"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
print(graph2)

png(file = "OncePerWeekClassesOnly2.png", bg = "transparent", type = c("cairo"), width=1600, height=1800, res=300)

ggplot(comb.new, aes(x=Time, y=DistFromPrev)) +
  geom_point(aes(size=freq), alpha=0.2, show.legend = F, colour="grey")+
  geom_smooth(method=lm, se=F, fullrange=TRUE,  formula= y~ x+I(x^2),colour="gray55", )+
  geom_smooth(data=sub, aes(x=Time, y=DistFromPrev),  formula= y~ x+I(x^2),method=lm, se=F, fullrange=TRUE, colour="gray30", linetype="dotdash")+
  geom_point(data = graph2, aes(x=Time, y=dep.avg), size=3.5, shape=17)+
  # facet_grid(Year~.)+
  theme(panel.background= element_rect(fill=NA), 
        plot.background = element_rect(fill=NA, colour=NA),
        axis.ticks.x=element_blank(),
        panel.border = element_rect(fill="transparent", colour="grey60"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  # geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="black", linetype="dotted")+
  # geom_smooth(method=lm, formula=y ~ poly(x,2), colour="maroon", se=T, fullrange=TRUE)+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1)
                       , limits=c(0,5))

dev.off()

```

#### By Class (Scatterplot + Means)

```{r}
comb_table<-count(comb.c, c("Year", "Time", "DistFromPrev"))
comb.new<-merge(comb.c, comb_table, by=c("Year", "Time", "DistFromPrev"), all.x=T, all.y=F)

graph1=ddply(comb.c, c("ID", "Time", "Year", "ClassType"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
graph2=ddply(graph1, c("Time", "Year", "ClassType"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
print(graph2)

png(file = "Figure2B.png", bg = "transparent", type = c("cairo"), width=2000, height=1800, res=300)

label <- c(F2014="Class 1 (Twice/Week)", W2016="Class 2 (Twice/Week)", F2015="Class 3 (Once/Week)", W2015="Class 4 (Once/Week)")

ggplot(graph2, aes(x=Time, y=dep.avg, group=Year))+   
  geom_point(data=comb.new, aes(x=Time, y=DistFromPrev, size=freq), alpha=0.15, show.legend = F, colour="grey")+
  geom_smooth(data=comb.c, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="gray55", )+
  geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="gray30", linetype="dotdash")+
  geom_point(size=3, shape=17, position = position_dodge(0.5), aes(colour=ClassType))+
  facet_wrap(.~Year, ncol=2, labeller=labeller(Year = label))+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="#432620"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="grey60"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="#432620"),
    legend.key = element_rect(fill = "transparent", colour = "transparent"),
    strip.background = element_rect(colour="gray60", fill="transparent")
  )+
  scale_colour_manual("Class Type", values=c("gray15","gray60"))+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1))

dev.off()

```


#### By Class (Scatterplot + Means); Curvilinear 

```{r}
comb_table<-count(comb.c, c("Year", "Time", "DistFromPrev"))
comb.new<-merge(comb.c, comb_table, by=c("Year", "Time", "DistFromPrev"), all.x=T, all.y=F)

graph1=ddply(comb.c, c("ID", "Time", "Year", "ClassType"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
graph2=ddply(graph1, c("Time", "Year", "ClassType"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
print(graph2)

label <- c(F2014="Class 1 (Twice/Week)", W2016="Class 2 (Twice/Week)", F2015="Class 3 (Once/Week)", W2015="Class 4 (Once/Week)")

png(file = "CurvilinearByClass.png", bg = "transparent", type = c("cairo"), width=2000, height=1800, res=300)

ggplot(graph2, aes(x=Time, y=dep.avg, group=Year))+   
  geom_point(data=comb.new, aes(x=Time, y=DistFromPrev, size=freq), alpha=0.15, show.legend = F, colour="grey")+
  geom_smooth(data=comb.c, aes(x=Time, y=DistFromPrev), method=lm, formula = y ~ x + I(x^2), se=F, fullrange=TRUE, colour="gray55", )+
  geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, formula = y ~ x + I(x^2), se=F, fullrange=TRUE, colour="gray30", linetype="dotdash")+
  geom_point(size=3, shape=17, position = position_dodge(0.5), aes(colour=ClassType))+
  facet_wrap(.~Year, ncol=2, labeller=labeller(Year = label))+
  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="#432620"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="grey60"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="#432620"),
    legend.key = element_rect(fill = "transparent", colour = "transparent"),
    strip.background = element_rect(colour="gray60", fill="transparent")
  )+
  scale_colour_manual("Class", values=c("gray15","gray60"))+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1))

dev.off()


```




### Repetition 

```{r}
int<-lmer(DistFromPrev~Time+Order+Time2*ClassFreq+(1|UserName), data = comb.c, REML=F, na.action="na.omit")
summary(int)
confint(int, method="Wald")
```

#### Linear Effects

```{r}
int.lin<-lmer(DistFromPrev~Time+Order+Time2*ClassFreq+(1|UserName), data = sub, REML=F, na.action="na.omit")
summary(int.lin)
```

#### Curvilinear Effects
```{r}
final<-subset(lecex, ExamType=="Final")
fin.m<-melt(final, id=c(1:10, 12:20))
fin.cast<-dcast(fin.m, ID+UserName+ClassFreq+Year~ClassType)


equal<-subset(comb.c, comb.c$Time %in% unique(comb.c$Time[comb.c$ClassFreq=="Once"]))

int2<-lmer(DistFromPrev~Time+Order+Time2*ClassFreq+(1|UserName), data = equal, REML=F, na.action="na.omit")
summary(int2)
confint(int2, method="Wald")


equal.sub<-subset(equal, equal$FinalExam=="No")

int<-NULL
for (id in levels(sub$ID)){
  subs<-sub[sub$ID==id,]
  subs.eq<-equal.sub[equal.sub$ID==id,]
  if (nrow(subs)<4){
    next
  } else {
    mod<-lm(DistFromPrev~Time+Order, data = subs, na.action="na.omit")
    coef<-mod$coefficients
    se<-coef(summary(mod))[, 2]
    time<-data.frame(ID=id, ClassFreq=subs$ClassFreq[1], Obs=nrow(subs), as.data.frame(cbind(coef, se))[2,])
  }
  if (nrow(subs.eq)<4){
    next
  } else {
    mod.eq<-lm(DistFromPrev~Time+Order, data = subs.eq, na.action="na.omit")
    coef.eq<-mod.eq$coefficients
    se.eq<-coef(summary(mod.eq))[, 2]
    time.eq<-data.frame(Obs.eq=nrow(subs.eq), as.data.frame(cbind(coef.eq, se.eq))[2,])
  }
  both<-cbind(time, time.eq)
  int<-rbind(int, both)
}

finint<-merge(int, fin.cast[c(1,2,6)], by="ID", all.x=T, all.y=F)

des<-cbind(ddply(sub, .(ID), function(df)
  return(c(Avg=mean(df$DistFromPrev, na.rm=T),
           SD=sd(df$DistFromPrev, na.rm=T),
           Count=length(df$DistFromPrev)))),
  ddply(equal.sub, .(ID), function(df)
  return(c(Avg.eq=mean(df$DistFromPrev, na.rm=T),
           SD.eq=sd(df$DistFromPrev, na.rm=T),
           Count.eq=length(df$DistFromPrev)))))[-c(5)]
des2<-des[complete.cases(des),]

finint<-merge(finint, des2, by="ID", all.x=T, all.y=F)


# Model with coef as predictor
fin.mod<-lm(Exam~coef.eq+Avg.eq, data=finint)

# Model with se as redictor
fin.mod2<-lm(Exam~se.eq+Avg.eq+SD.eq, data=finint)

# Model with SD as predictor
fin.mod3<-lm(Exam~SD.eq+Avg.eq, data=finint)

t.test(finint$Exam~finint$ClassFreq)

ggplot(finint2, aes(x=se.eq, y=Exam, group=ClassFreq, colour=ClassFreq)) +
  geom_point()+
  geom_smooth(method=lm, se=T, fullrange=TRUE)

ggplot(finint2, aes(x=coef, y=Exam, group=ClassFreq, colour=ClassFreq)) +
  geom_point()+
  geom_smooth(method=lm, se=T, fullrange=TRUE)

```


#### By Class FREQUENCY (Scatterplot + Means); 

```{r}
comb_table<-count(equal, c("Time", "ClassFreq", "DistFromPrev"))
comb.new<-merge(equal, comb_table, by=c("Time", "ClassFreq", "DistFromPrev"), all.x=T, all.y=F)

graph1=ddply(comb.new, c("ID", "Week", "ClassFreq"), function(df) 
  return(c(dep.avg=mean(df$DistFromPrev, na.rm=T)))) # change DV
# head(graph1)
graph2=ddply(graph1, c("Week", "ClassFreq"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))
# print(graph2)

label <- c(Once="Once/Week", Twice="Twice/Week")

# png(file = "Classroom_Figure3.png", bg = "transparent", type = c("cairo"), width=2200, height=1400, res=300)

ggplot(comb.new, aes(x=Time, y=DistFromPrev)) +
  geom_point(aes(size=freq), alpha=0.2, show.legend = F, colour="grey")+
  geom_smooth(method=lm, formula = y ~ x + I(x^2), se=F, fullrange=TRUE, colour="gray55")+
  geom_smooth(data=equal.sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="gray30", linetype="dotdash")+
  geom_point(data = graph2, aes(x=Week, y=dep.avg), size=3.5, shape=17)+
  facet_grid(.~ClassFreq)+
  theme(panel.background= element_rect(fill=NA), 
        plot.background = element_rect(fill=NA, colour=NA),
        axis.ticks.x=element_blank(),
        panel.border = element_rect(fill="transparent", colour="grey60"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.margin=unit(c(.5,.5,0.5,.5), "cm"))+
  # geom_smooth(data=sub, aes(x=Time, y=DistFromPrev), method=lm, se=F, fullrange=TRUE, colour="black", linetype="dotted")+
  # geom_smooth(method=lm, formula=y ~ poly(x,2), colour="maroon", se=T, fullrange=TRUE)+
  scale_x_continuous("Time (Days)")+
  scale_y_continuous("Distance from Previous Seat (m)",  breaks=seq(0, 10, 1))+
  coord_cartesian(xlim=c(0,88))

# dev.off()


```




## subset of data set that includes individuals that attended more than 1 of the 4 courses

```{r}
id<-unique(comb.c$ID)
ID<-data.frame(ID=id, UserName=substr(id, 1, nchar(as.character(id))-5))
dup<-ID$UserName[duplicated(ID$UserName)]

duplicate<-ID[ID$UserName %in% dup,]
duplicate<-duplicate[order(duplicate$UserName),]
duplicate$ClassOrder<-factor(c("First", "Second"))

repeats<-merge(comb.c[comb.c$UserName %in% dup,], duplicate, by="ID", all.x=T, all.y=F)

r2<-subset(repeats, FinalExam=="No")

cross<-lme(DistFromPrev~Time+Order+Time2*ClassOrder, random = ~1|ID, data = repeats, method="ML", na.action=na.omit)
summary(cross)
```





# ADDITIONAL ANALYSES


```{r}
order<-ddply(comb.c, .(ID), summarise, 
             mean.order=mean(Order), 
             sd.order=sd(Order),
             n.order=length(Order))

sub.o<-subset(order, n.order>3)
sub.o2<-subset(sub.o, mean.order>5)


graph2=ddply(graph1, c("Week", "ClassFreq"), function(df)  
  return(c(dep.avg=mean(df$dep.avg, na.rm=T), dep.sd=sd(df$dep.avg, na.rm=T), dep.count=length(df$dep.avg), dep.sem=(sd(df$dep.avg, na.rm=T))/(sqrt(length(df$dep.avg))))))

```

```{r}
new<-comb.c

new$Dist<-ifelse(new$DistFromPrev<1.5, "Short", "Long")

graph2<-ddply(new, .(ID), summarise,
              meanDist=mean(DistFromPrev, na.rm=T),
              sdDist=sd(DistFromPrev, na.rm=T),
              meanOrder=mean(Order, na.rm=T),
              sdOrder=sd(Order, na.rm=T),
              count=length(DistFromPrev))

model<-lm(meanDist~meanOrder, data=graph2)
tab_model(model)

```





### Heat Map 

```{r}
ggplot(pos2, aes(x=X, y=Y) ) +
  facet_grid(IS_TARG~PrePost)+
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  theme_bw()+
  scale_fill_viridis()+
  scale_x_continuous("Position (X-Cordinate)", expand = c(0, 0)) +
  scale_y_continuous("Position (Y-Cordinate)", expand = c(0, 0)) +
  theme(
    # legend.position='none'
  )
```



### Additional Analysis






